---
title: Starting with R codes in tidyverse
author: Ruoran Li
date: '2018-05-04'
slug: try-r-codes-and-plots
categories:
  - Learn R
tags:
  - R
  - tidyverse
  - workflow
---

# Set up

I'm following the [R for data science book](http://r4ds.had.co.nz/) to learn some better practices for organizing my analyses. My motivation for this is that I've only just realized that I have been using base R for most of my previous data cleaning works -- maybe I should start learning to use packages that can simplify this process. 

`tidyverse` may be the place to start (heard about it from Roger Peng and Hilary Parker's [podcast](http://nssdeviations.com/)). 

```{r}
library(tidyverse)
```

One important distinction is that each R project should be self-contained. Lessons learned form [this post on project-oriented workflow](https://www.tidyverse.org/articles/2017/12/workflow-vs-script/):

+ Use relative paths, and do not `setwd()`. 
+ Open new sessions for each research question, and do not `rm(list=ls())`. 

# Chapter 3. Data visualization

Following the book's progress, using the mpg data from ggplot2.
```{r}
mpg
```

Showing some simple visualization before I move on to tackle more complicated problems: 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```
Until next time!